Local PCA Shows How Population Structure Differs Along the Genome

### 2016-05-27 writeup/local_pca_paper.tex
two more refs

\paragraph{Chromosomal inversions}
A major driver of variation in population structure in two datasets we examined are inversions.
This may be common,
but the example of \textit{Medicago truncatula} shows that polymorphic inversions are not ubiquitous.
PCA has been proposed as a method for discovering inversions \citep{ma_identify_inversions};
However, the signal left by inversions likely cannot be distinguished from long haplotypes under balancing selection 
or simply regions of reduced recombination.
However, in many applications, inversions are a nuisance.
For instance, SMARTPCA \citep{smartpca} reduces their effect on PCA plots
by regressing out the effect of linked SNPs on each other.
It would be interesting to see if smoehow removing the effects of inversions in the \textit{Drosophila melanogaster} or human datasets
would produce a pattern similar to that seen in \textit{Medicago truncatula}.

>>>>

\paragraph{Chromosomal inversions}
A major driver of variation in population structure in two datasets we examined are inversions.
This may be common,
but the example of \textit{Medicago truncatula} shows that polymorphic inversions are not ubiquitous.
PCA has been proposed as a method for discovering inversions \citep{ma2012investigation};
However, the signal left by inversions likely cannot be distinguished from long haplotypes under balancing selection 
or simply regions of reduced recombination.
However, in many applications, inversions are a nuisance.
For instance, SMARTPCA \citep{patterson2006population} reduces their effect on PCA plots
by regressing out the effect of linked SNPs on each other.
It would be interesting to see if smoehow removing the effects of inversions in the \textit{Drosophila melanogaster} or human datasets
would produce a pattern similar to that seen in \textit{Medicago truncatula}.
